Bootstrap Confidence Intervals for Regression Discontinuity Designs with Uniform Kernels

### 2016-02-25 main_paper.tex
Small changes to text and latex code in Sections 2 and 3. Still not happy with it though.

In the typical sharp RD setting, a researcher wishes to estimate the local 
causal effect of treatment at a given threshold. The running variable, $X_{i}$, 
determines treatment assignment.  Given a known threshold, $\bar{x}$, set to 
zero without loss of generality, a unit receives treatment if $X_{i} \geq 0$ or 
does not receive treatment if $X_{i} < 0$. Let $Y_{i}(1)$ and $Y_{i}(0)$ denote 
the potential outcomes for unit $i$ given it receives treatment and
 in the absence of treatment, respectively. Hence, the observed sample is 
 comprised of the running variable, $X_{i}$, and
 \begin{align}
  Y_{i}=Y_{i}(0) \1\{X_{i}<0\}+Y_{i}(1) \1\{X_{i} \geq 0\}
 \end{align}
where $\1\{ \cdot\}$ denotes the indicator function. For convenience,
define
 \begin{align}
  \mu(x)= \E[Y_{i} \mid X_{i}=x]
 \end{align}
Also, let $\mu^{(\eta)}(x)=\frac{d^{\eta}\mu(x)}{dx^{\eta}}$ be the $\eta^{th}$ 
derivative of the unknown regression function and define 
$\mu^{(\eta)}_{+}=lim_{x \rightarrow 0^{+}}\mu^{(\eta)}(x)$ and 
$\mu^{(\eta)}_{-}=lim_{x \rightarrow 0^{-}}\mu^{(\eta)}(x)$.
In most cases the population parameter of interest is 
$\tau=\E[Y(1)-Y(0) \mid X=\bar{x}]$ (i.e., the average treatment effect
at the threshold). Under continuity and smoothness conditions on both the 
conditional distribution of $X_i$ and the first moments of $Y(0)$ and $Y(1)$ at
the cutoff, $\tau$ is nonparametrically identifiable
$\tau = \mu_{+}- \mu_{-}$
where $\mu_{+}=lim_{x \rightarrow 0^{+}}\mu(x)$ and
$\mu_{-}=lim_{x \rightarrow 0^{-}}\mu(x)$
(Hahn, Todd and Van der Klaauw, 2001)

Naturally, the estimation of $\tau$ in RD designs focuses on the 
problem of approximating $\E[Y(1) \mid X=x]$ and $\E[Y(0) \mid X=x]$
near the cutoff. Due to its desirable properties when estimating regression 
functions at boundary points, we consider the popular approach of fitting 
local linear regressions in neighborhoods on both
sides of the threshold.\footnote{See \cite{HTV2001}, \cite{Porter03} or
\cite{FanGijbels92} for discussions of the properties of local polynomial 
regressions for boundary problems.The results presented here are valid for
higher order polynomials and discontinuities at derivatives, like ``Kink RDD''. We focus on the linear case for ease in exposition.}
For the local linear model, we use the following estimator as described in 
\cite{calonico2014},\footnote{Throughout the paper we follow the
notation on CCT very closely.}
\begin{align*}
 \hat{\tau}(h_{n})&=\hat {\mu}_{+}(h_{n}) -\hat{\mu}_{-}(h_{n})\\
(\hat {\mu}_{+}(h_{n}),\hat {\mu}^{(1)}_{+}(h_{n}))'&= \argmin_{b_{0},b_{1}}
\sum_{i=1}^{N}\1\{h_n > X_{i} \geq 0\}(Y_{i}-b_{0}-X_{i}b_{1})^{2} \\
(\hat {\mu}_{-}(h_{n}),\hat {\mu}^{(1)}_{-}(h_{n}))' &= \argmin_{b_{0},b_{1}}
\sum_{i=1}^{N}\1\{0 > X_{i} > -h_n \}(Y_{i}-b_{0}-X_{i}b_{1})^{2}
\end{align*}

As shown by \cite{HTV2001}, \cite{Porter03} and expanded by CCT identification and inference procedures can be developed based on the following assumptions\footnote{The assumptions below are the same as presented by CCT.}

\begin{assumption}[Behavior of the DGP near the cutoff]\label{A1}
  The random variables $Y_i, X_i$ are i.i.d.\ and
  there exists a positive number $\kappa_0$ such that the following
  conditions hold for all $x$ in the neighborhood
  $(-\kappa_{0},\kappa_{0})$ around zero:
  \begin{enumerate}
  \item $\E[Y_{i}^{4} \mid X_{i}=x]$ is bounded and the density of $X$
    is continuous and bounded away from zero.
  \item $\mu_{+}(x) = \E[ Y_{i}(1) \mid X_{i}=x ]$ and
    $\mu_{-}(x) = \E[ Y_{i}(0) \mid X_{i}=x ]$ are $p+2$ times
    continuously differentiable.
  \item $\sigma^{2}_{+}(x)=\V[ Y_{i}(1) \mid X_{i}=x ]$ and
    $\sigma^{2}_{-}(x)=\V[ Y_{i}(0) \mid X_{i}=x ]$ are continuous and
    bounded away from zero.
 \end{enumerate}
\end{assumption}

@@

\begin{assumption}[Bandwidth]\label{A2}
  Let $h_n$ be the bandwidth used to estimate the local linear model and let
  $b_n$ be the bandwidth used for a local quadratic model. Then
  $n h_n \to \infty$, $n b_n \to \infty$, $n h_n^5 b_n^2 \to 0$, and
  $n b_n^5 h_n^2 \to 0$ as $n \to \infty$.\footnote{%
    Unless otherwise stated, all limits in this paper are assumed to hold as
    $n \to \infty$.} %
  The relationship $h_n \leq b_n$ also holds for all $n$.
\end{assumption}

\cite{calonico2014} point out that the conventional approaches to construct confidence intervals for $\tau$ using the local linear estimator rely on a large-sample approximation for the standardized $t$-statistic that is valid only if the bandwidth shrink fast enough to eliminate the leading bias term contribution to the approximation. Hence, if $nh_{n}^{5}\rightarrow0$ and $nh_{n}\rightarrow \infty$, then
 \begin{align}
  T(h_{n}) &=\frac{\hat{\tau}(h_{n})-\tau}{\sqrt{V(h_{n})}}\rightarrow_{d}N(0,1), &
  V(h_{n}) &=\V[\tau(h_{n}) \mid X_1,\dots,X_n]
 \end{align}
 The conditional variance $V(h_{n})$ depends on the $\sigma^{2}_{+}=lim_{x \rightarrow 0^{+}}\sigma^{2}_{+}(x)$ and $\sigma^{2}_{-}=lim_{x \rightarrow 0^{-}}\sigma^{2}_{-}(x)$ as well as $h_{n}$ and known quantities that depend on the kernel and order of polynomial used in the estimation. Under these conditions we could use a conventional confidence interval for $\tau$ given by
 \begin{align}
  I(h_{n})=\left[\hat{\tau}(h_{n})\pm \Phi^{-1}_{1-\frac{\alpha}{2}}\sqrt{V(h_{n})} \right]
 \end{align}
with $\Phi^{-1}_{1-\frac{\alpha}{2}}$ being the $\alpha$-quantile of the standard normal distribution. However, most approaches to select the bandwidth, $h_{n}$ in the literature, including the widely used optimal-AMSE bandwidth selector proposed by \cite{IK} lead to bandwidth choices that are ``too large'' since they do not satisfy the condition $nh_{n}^{5}\rightarrow0$, leading to a first-order bias in the distributional approximation used to construct the confidence intervals.

\cite{calonico2014} resolve the problem by deriving the analytical form of the first-order bias and correcting it directly. To obtain correct coverage the confidence interval needs not only to be re-centered to correct the bias, but also rescaled to allow for the additional variability introduced by the bias correction. Their approach relies on obtaining a bias-corrected  estimator, $\hat{\tau}^{bc}$ and its adjusted variance. It is important first to note that the first-order bias term itself will depend on the bandwidth $h_{n}$. The approximate bias term can be described as:
\begin{align*}
     \E[\hat{\tau}(h_{n}) \mid \chi_{n}]-\tau=& h_{n}^{2}\Bs(h_{n})\{1+o_{p}(1)\}\\
     \Bs(h_{n})=&\frac{\mu_{+}^{(2)}}{2!}\Bf_{+}(h_{n})-\frac{\mu_{-}^{(2)}}{2!}\Bf_{-}(h_{n})
   \end{align*}
where $\Bf_{+}(h_{n})$ and $\Bf_{-}(h_{n})$ are observed quantities that depend on the data, kernel and $h_{n}$. The plug-in bias-corrected estimator then requires estimates for the second derivatives of the conditional mean from above and below the cutoff, $\mu_{+}^{(2)}$ and $\mu_{-}^{(2)}$. CCT propose using a conventional local quadratic estimator, i.e. one order higher than the polynomial used to obtain $\hat{\tau}$,  using a (potentially) different pilot bandwidth $b_{n}$.
\begin{align*}
     \hat{\tau}^{bc}(h_{n}, b_{n})=& \hat{\tau}-h_{n}^{2}\hat{\Bs}(h_{n},b_{n})\\
     \hat{\Bs}(h_{n})=&\frac{\hat{\mu}_{+}^{(2)}(b_{n})}{2!}\Bf_{+}(h_{n})-\frac{\hat{\mu}_{-}^{(2)}(b_{n})}{2!}\Bf_{-}(h_{n})
   \end{align*}
By incorporating the contribution of both $\hat{\tau}(h_{n})$ and $\hat{\Bs}(h_{n},b_{n})$ to the asymptotic distribution of the estimator, CCT obtain a robust confidence interval with a different asymptotic variance in general. So under Assumptions \ref{A1} and \ref{A2}, if $n\min\{h_{n}^{5}, b_{n}^{5}\}max\{h_{n}^{2}, b_{n}^{2}\}\rightarrow 0$ and $n\min\{h_{n}, b_{n}\}\rightarrow \infty$ and $\kappa \max\{h_{n},b_{n}\}< \kappa_{0}$, they show that
\begin{align}
  T^{rbc}(h_{n}, b_{n})=\frac{\hat{\tau}^{bc}(h_{n}, b_{n})-\tau}{\sqrt{V^{bc}(h_{n}, b_{n})}}\rightarrow_{d}N(0,1), \text{        }V^{bc}(h_{n}, b_{n})=V(h_{n})+C^{bc}(h_{n}, b_{n})\\
 \end{align}
where the additional term $C^{bc}(h_{n}, b_{n})$ depends on the (asymptotic) variability of the bias estimate used for correction as well as its correlation with the original RD estimator $\hat{\tau}(h_{n})$.\footnote{The details of the formulas are currently ommitted from this paper since their form is not relevant to the bootstrap procedure innovation proposed. The details can be found at CCT Appendix.}  Under these conditions we can construct a valid confidence interval for $\tau$ given by
 \begin{align}
  I^{rbc}(h_{n}, b_{n})=\left[\left(\hat{\tau}(h_{n})-h_{n}^{2}\hat{\Bs}(h_{n},b_{n})\right)\pm \Phi^{-1}_{1-\frac{\alpha}{2}}\sqrt{V(h_{n})+C^{bc}(h_{n}, b_{n})} \right]
 \end{align}

This approach is shown by the authors to significantly improve coverage of the CIs constructed and provides practitioners with a new tool set to perform inference that is more robust to the choice of bandwidth. We build upon the insight provided by CCT bias-corrected estimator and propose a simple bootstrap procedure that can directly construct the robust CIs without requiring the derivation of analytical formulas and direct estimators for the bias, variance and covariance terms, while relying on the same first-order bias correction approximation proposed by that paper.

@@

Building upon the results and intuition developed by CCT we propose to implement a first-order bias correction and obtain valid CIs through a bootstrap procedure.
Intuitively, for the local-linear RD estimator's case, we will rely on a local higher-order (quadratic) polynomial approximation for the conditional outcome around the cutoff to capture the potential bias present in the original RD estimate. This insight comes directly from CCT using the same local quadratic approximation to estimate bias term as presented in Section \ref{background}.

The first algorithm describes how to use local linear regression to obtain a point estimate and perform bias correction with local quadratic regression. The second algorithm describes how to obtain its confidence interval with correct coverage. For simplicity, we adopt the same optimal-AMSE bandwidth selector proposed by CCT.\footnote{An interesting question is whether one could use a bootstrap based procedure to select a bandwidth that would achieve similar (or improved) results. This is beyond the scope of this particular paper but is part of ongoing research effort.}

Essentially, we apply CCT's insight that a polynomial one order higher can capture the first-order bias behavior and create a bootstrap procedure that can correctly mimic the behavior of the bias present in the original estimator. For such, for a chosen bandwidth, we estimate a local quadratic regression the same way CCT suggested but then create bootstrap data by imposing the local quadratic functional form as the DGP. Then, in the ``bootstrap data'' the DGP is known. Let the ``true'' treatment effect under the bootstrap DGP be denoted by $\tau^{*}$. We then estimate the treatment effect using the (misspecified) local linear estimator, $\hat{\tau}^{*}$ to the generated data. Hence, the bias for a specific bootstrap data is given by $\tau^{*}-\hat{\tau}^{*}$. More importantly, by generating new bootstrapped data based on the same quadratic DGP and its residual's distribution, we can obtain an estimate of the first-order bias (the part that is captured by $\hat{\Bs}(h_{n},b_{n})$ in CCT's formulas on Section \ref{background}) in the original estimate by averaging across the bias in all $B$ bootstrapped data estimates,i.e., $\tau^{*} - \sum_{i = 1}^{B} \hat{\tau}_{ i}^{*}$. Algorithm~\ref{Alg1} describes this procedure step-by-step for clarity.

\begin{algorithm}[Bias estimation]\label{Alg1}
  Assume $h_n$ and $b_n$ are bandwidths as described by Assumption~\ref{A2} and
  define
  \begin{align}
    I^-(h) &= \{i : h < X_i < 0\}, &
    I^+(h) &= \{i : 0 < X_i < h\}.
  \end{align}
  Also define $M^-(h_n)$ and $M^+(h_n)$ to be the number of elements in
  $I^-(h_n)$ and $I^+(h_n)$ respectively.
  \begin{enumerate}
  \item Estimate the local polynomials $g_{p+1}^+$ and $g_{p+1}^-$ as defined by
    Equation --- and define the residuals
    \begin{equation}
      \label{eq:1}
      \hat\varepsilon_i =
      \begin{cases}
        Y_i - \hat g_{p+1}^-(X_i) & \textif\ X_i < 0 \\
        Y_i - \hat g_{p+1}^+(X_i) & \otherwise
      \end{cases}
    \end{equation}
  \item Repeat the following steps $B_1$ times to produce a sequence of bootstrap
    estimates $\hat\tau_1^*,\dots,\hat\tau_{B_1}^*$. For the $k$th step:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M^-(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^-(b_n)\}$ and one of size $M^+(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^+(h_n)\}$. Let $\varepsilon_i^{*-}$ and
      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
      \begin{align}
        Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
        Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
      \end{align}
    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
      \begin{align}
        \hat\mu_-^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^-(h_n)} (Y_i^{*-} -
          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta_p (X_i^{*-})^p))^2 \\
        \hat\mu_+^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^+(h_n)} (Y_i^{*+} -
          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta_p (X_i^{*+})^p))^2
      \end{align}
    \item Save $\hat\mu_+^* - \hat\mu_-^*$ as $\hat\tau^*_k$.
    \end{enumerate}
  \item Estimate the bias as
    \begin{equation}
      \label{eq:2}
      \Delta^* = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k -
      \big[\hat g_{p+1}^+(0) - \hat g_{p+1}^-(0)\big]
    \end{equation}
  \end{enumerate}
\end{algorithm}
Obviously, the distribution of $\Delta^*$ depends on $B_1$ and we could
incorporate that dependency into our notation by wrting
$\Delta^*_{B_1}$. However, we will follow standard practice in the bootstrap
literature and assume that $B_1$ is large enough that it can be ignored and
define $\Delta^* = \plim_{B_1 \to \infty} \Delta^*_{B_1}$

>>>>

In the typical sharp RD setting, a researcher wishes to estimate the local 
causal effect of treatment at a given threshold. The running variable, $X_{i}$, 
determines treatment assignment.  Given a known threshold, $\bar{x}$, set to 
zero without loss of generality, a unit receives treatment if $X_{i} \geq 0$ or 
does not receive treatment if $X_{i} < 0$. Let $Y_{i}(1)$ and $Y_{i}(0)$ denote 
the potential outcomes for unit $i$ given it receives treatment and
 in the absence of treatment, respectively. Hence, the observed sample is 
 comprised of the running variable, $X_{i}$, and
 \begin{align}
  Y_{i}=Y_{i}(0) \1\{X_{i}<0\}+Y_{i}(1) \1\{X_{i} \geq 0\}
 \end{align}
where $\1\{ \cdot\}$ denotes the indicator function. For convenience,
define
 \begin{align}
  \mu(x)= \E[Y_{i} \mid X_{i}=x]
 \end{align}
Also, let $\mu^{(\eta)}(x)=\frac{d^{\eta}\mu(x)}{dx^{\eta}}$ be the $\eta^{th}$ 
derivative of the unknown regression function and define 
$\mu^{(\eta)}_{+}=lim_{x \rightarrow 0^{+}}\mu^{(\eta)}(x)$ and 
$\mu^{(\eta)}_{-}=lim_{x \rightarrow 0^{-}}\mu^{(\eta)}(x)$.
In most cases the population parameter of interest is 
$\tau=\E[Y(1)-Y(0) \mid X=\bar{x}]$ (i.e., the average treatment effect
at the threshold). Under continuity and smoothness conditions on both the 
conditional distribution of $X_i$ and the first moments of $Y(0)$ and $Y(1)$ at
the cutoff, $\tau$ is nonparametrically identifiable by
$\tau = \mu_{+}- \mu_{-}$
where $\mu_{+}=lim_{x \rightarrow 0^{+}}\mu(x)$ and
$\mu_{-}=lim_{x \rightarrow 0^{-}}\mu(x)$
(Hahn, Todd and Van der Klaauw, 2001)

Naturally, the estimation of $\tau$ in RD designs focuses on the 
problem of approximating $\E[Y(1) \mid X=x]$ and $\E[Y(0) \mid X=x]$
near the cutoff. Due to its desirable properties when estimating regression 
functions at boundary points, we consider the popular approach of fitting 
local linear regressions in neighborhoods on both
sides of the threshold.\footnote{See \cite{HTV2001}, \cite{Porter03} or
\cite{FanGijbels92} for discussions of the properties of local polynomial 
regressions for boundary problems.The results presented here are valid for
higher order polynomials and discontinuities at derivatives, like ``Kink RDD''. We focus on the linear case for ease in exposition.}
For the local linear model,
\begin{align*}
 \hat{\tau}(h_{n})&=\hat {\mu}_{+}(h_{n}) -\hat{\mu}_{-}(h_{n})\\
(\hat {\mu}_{+}(h_{n}),\hat {\mu}^{(1)}_{+}(h_{n}))'&= \argmin_{b_{0},b_{1}}
\sum_{i=1}^{N}\1\{h_n > X_{i} \geq 0\}(Y_{i}-b_{0}-X_{i}b_{1})^{2} \\
(\hat {\mu}_{-}(h_{n}),\hat {\mu}^{(1)}_{-}(h_{n}))' &= \argmin_{b_{0},b_{1}}
\sum_{i=1}^{N}\1\{0 > X_{i} > -h_n \}(Y_{i}-b_{0}-X_{i}b_{1})^{2}
\end{align*}

As shown by \cite{HTV2001}, \cite{Porter03} and expanded by CCT identification and inference procedures can be developed based on the following assumptions.\footnote{The assumptions below are the same as presented by CCT.}

\begin{assumption}[Behavior of the DGP near the cutoff]\label{A1}
  The random variables $Y_{i}, X_{i}$ are i.i.d.\ and
  there exists a positive number $\kappa_0$ such that the following
  conditions hold for all $x$ in the neighborhood
  $(-\kappa_{0},\kappa_{0})$ around zero:
  \begin{enumerate}
  \item $\E[Y_{i}^{4} \mid X_{i}=x]$ is bounded and the density of $X$
    is continuous and bounded away from zero.
  \item $\mu_{+}(x) = \E[ Y_{i}(1) \mid X_{i}=x ]$ and
    $\mu_{-}(x) = \E[ Y_{i}(0) \mid X_{i}=x ]$ are $p+2$ times
    continuously differentiable.
  \item $\sigma^{2}_{+}(x)=\V[ Y_{i}(1) \mid X_{i}=x ]$ and
    $\sigma^{2}_{-}(x)=\V[ Y_{i}(0) \mid X_{i}=x ]$ are continuous and
    bounded away from zero.
 \end{enumerate}
\end{assumption}

@@

\begin{assumption}[Bandwidth]\label{A2}
  Let $h_{n}$ be the bandwidth used to estimate the local linear model and let
  $b_{n}$ be the bandwidth used to estimate a local quadratic model. Then
  $n h_{n} \to \infty$, $n b_{n} \to \infty$, $n h_{n}^{5} b_{n}^{2} \to 0$, and
  $n b_{n}^{5} h_{n}^{2} \to 0$ as $n \to \infty$.\footnote{%
    Unless otherwise stated, all limits in this paper are assumed to hold as
    $n \to \infty$.} %
  The relationship $h_{n} \leq b_{n}$ also holds for all $n$.
\end{assumption}

CCT point out that the conventional approaches to construct confidence intervals for $\tau$ using the local linear estimator rely on a large-sample approximation for the standardized $t$-statistic that is valid only if the bandwidth shrink fast enough to eliminate the leading bias term contribution to the approximation. Hence, if $nh_{n}^{5}\rightarrow0$ and $nh_{n}\rightarrow \infty$, then
 \begin{align}
  T(h_{n}) &=\frac{\hat{\tau}(h_{n})-\tau}{\sqrt{V(h_{n})}}\rightarrow_{d}N(0,1), &
  V(h_{n}) &=\V[\tau(h_{n}) \mid X_{1},\dots,X_{n}]
 \end{align}
 The conditional variance $V(h_{n})$ depends on the $\sigma^{2}_{+}=lim_{x \rightarrow 0^{+}}\sigma^{2}_{+}(x)$ and $\sigma^{2}_{-}=lim_{x \rightarrow 0^{-}}\sigma^{2}_{-}(x)$ as well as $h_{n}$ and known quantities that depend on the kernel and order of polynomial used in the estimation. Under these conditions we could use a conventional confidence interval for $\tau$ given by
 \begin{align}
  I(h_{n})=\left[\hat{\tau}(h_{n})\pm \Phi^{-1}_{1-\frac{\alpha}{2}}\sqrt{V(h_{n})} \right]
 \end{align}
with $\Phi^{-1}_{1-\frac{\alpha}{2}}$ being the $\alpha$-quantile of the standard normal distribution. However, most approaches to select the bandwidth, $h_{n}$ in the literature, including the widely used optimal-AMSE bandwidth selector proposed by \cite{IK} lead to bandwidth choices that are ``too large'' since they do not satisfy the condition $nh_{n}^{5}\rightarrow0$, leading to a first-order bias in the distributional approximation used to construct the confidence intervals.

CCT solve the problem by deriving the analytical form of the first-order bias and correcting it directly. To obtain correct coverage the confidence interval needs not only to be re-centered to correct the bias, but also rescaled to allow for the additional variability introduced by the bias correction. Their approach relies on obtaining a bias-corrected  estimator, $\hat{\tau}^{bc}$ and its adjusted variance. It is important first to note that the first-order bias term itself will depend on the bandwidth $h_{n}$. The approximate bias term can be described as:
\begin{align*}
     \E[\hat{\tau}(h_{n}) \mid \chi_{n}]-\tau=& h_{n}^{2}\Bs(h_{n})\{1+o_{p}(1)\}\\
     \Bs(h_{n})=&\frac{\mu_{+}^{(2)}}{2!}\Bf_{+}(h_{n})-\frac{\mu_{-}^{(2)}}{2!}\Bf_{-}(h_{n})
   \end{align*}
where $\Bf_{+}(h_{n})$ and $\Bf_{-}(h_{n})$ are observed quantities that depend on the data, kernel and $h_{n}$. The plug-in bias-corrected estimator then requires estimates for the second derivatives of the conditional mean from above and below the cutoff, $\mu_{+}^{(2)}$ and $\mu_{-}^{(2)}$. CCT propose using a conventional local quadratic estimator, i.e. one order higher than the polynomial used to obtain $\hat{\tau}$,  using a (potentially) different pilot bandwidth $b_{n}$.
\begin{align*}
     \hat{\tau}^{bc}(h_{n}, b_{n})=& \hat{\tau}-h_{n}^{2}\hat{\Bs}(h_{n},b_{n})\\
     \hat{\Bs}(h_{n})=&\frac{\hat{\mu}_{+}^{(2)}(b_{n})}{2!}\Bf_{+}(h_{n})-\frac{\hat{\mu}_{-}^{(2)}(b_{n})}{2!}\Bf_{-}(h_{n})
   \end{align*}
By incorporating the contribution of both $\hat{\tau}(h_{n})$ and $\hat{\Bs}(h_{n},b_{n})$ to the asymptotic distribution of the estimator, CCT obtain a robust confidence interval with a different asymptotic variance in general. So under Assumptions \ref{A1} and \ref{A2}, if $n\min\{h_{n}^{5}, b_{n}^{5}\}max\{h_{n}^{2}, b_{n}^{2}\}\rightarrow 0$ and $n\min\{h_{n}, b_{n}\}\rightarrow \infty$ and $\kappa \max\{h_{n},b_{n}\}< \kappa_{0}$, they show that
\begin{align}
  T^{rbc}(h_{n}, b_{n})=\frac{\hat{\tau}^{bc}(h_{n}, b_{n})-\tau}{\sqrt{V^{bc}(h_{n}, b_{n})}}\rightarrow_{d}N(0,1), \text{        }V^{bc}(h_{n}, b_{n})=V(h_{n})+C^{bc}(h_{n}, b_{n})\\
 \end{align}
where the additional term $C^{bc}(h_{n}, b_{n})$ depends on the (asymptotic) variability of the bias estimate used for correction as well as its correlation with the original RD estimator $\hat{\tau}(h_{n})$.\footnote{The details of the formulas are currently ommitted from this paper since their form is not relevant to the bootstrap procedure innovation proposed. The details can be found at CCT Appendix.}  Under these conditions we can construct a valid confidence interval for $\tau$ given by
 \begin{align}
  I^{rbc}(h_{n}, b_{n})=\left[\left(\hat{\tau}(h_{n})-h_{n}^{2}\hat{\Bs}(h_{n},b_{n})\right)\pm \Phi^{-1}_{1-\frac{\alpha}{2}}\sqrt{V(h_{n})+C^{bc}(h_{n}, b_{n})} \right]
 \end{align}

This approach is shown by the authors to significantly improve coverage of the CIs constructed and provides practitioners with a new tool set to perform inference that is more robust to the choice of bandwidth. We build upon the insight provided by CCT bias-corrected estimator and propose a simple bootstrap procedure that can directly construct the robust CIs without requiring the derivation of analytical formulas and direct estimators for the bias, variance and covariance terms, while relying on the same first-order bias correction approximation.

@@

Building upon the results and intuition developed by CCT we propose to implement a first-order bias correction and obtain valid CIs through a bootstrap procedure.
Intuitively, for the local-linear RD estimator's case, we will rely on a local quadratic polynomial approximation for the conditional outcome around the cutoff to capture the potential bias present in the original RD estimate. This insight comes directly from CCT's results using the same local quadratic approximation to estimate bias term as presented in Section \ref{background}.

The first algorithm describes how to obtain a point estimate and perform the bias correction. The second algorithm obtains its confidence interval with correct coverage. For simplicity, we adopt the same optimal-AMSE bandwidth selector proposed by CCT.\footnote{An interesting question is whether one could use a bootstrap based procedure to select a bandwidth that would achieve similar (or improved) results. This is beyond the scope of this particular paper but is part of ongoing research effort.}

Essentially, we apply CCT's insight that a polynomial one order higher can capture the first-order bias behavior and create a bootstrap procedure that can correctly mimic the behavior of the bias present in the original estimator. For such, for a chosen bandwidth, we estimate a local quadratic regression as suggested by CCT, but then bootstrap data by imposing the local quadratic functional form as the DGP. Then, in the bootstrap data the DGP is known. Let the ``true'' treatment effect under the bootstrap DGP be denoted by $\tau^{*}$. We then estimate the treatment effect using the (misspecified) local linear estimator, $\hat{\tau}^{*}$ to the generated data. Hence, the bias for a specific bootstrap data is given by $\tau^{*}-\hat{\tau}^{*}$. More importantly, by generating new bootstrapped data based on the same quadratic DGP and its residual's distribution, we can obtain an estimate of the first-order bias (the part that is captured by $\hat{\Bs}(h_{n},b_{n})$ in CCT's formulas on Section \ref{background}) in the original estimate by averaging across the bias in all $B$ bootstrapped data estimates, i.e., $\tau^{*} - \sum_{i = 1}^{B} \hat{\tau}_{ i}^{*}$. Algorithm~\ref{Alg1} describes this procedure step-by-step for clarity.

\begin{algorithm}[Bias estimation]\label{Alg1}
  Assume $h_{n}$ and $b_{n}$ are bandwidths as described by Assumption~\ref{A2} and define
  \begin{align}
    I^{-}(h) &= \{i : h < X_{i} < 0\}, &
    I^{+}(h) &= \{i : 0 < X_{i} < h\}.
  \end{align}
  Also define $M^{-}(h_{n})$ and $M^{+}(h_{n})$ to be the number of elements in
  $I^{-}(h_{n})$ and $I^{+}(h_{n})$ respectively.
  \begin{enumerate}
  \item Estimate the local polynomials $g_{p+1}^{+}$ and $g_{p+1}^{-}$ as defined by
    Equation --- and define the residuals
    \begin{equation}
      \label{eq:1}
      \hat\varepsilon_{i} =
      \begin{cases}
        Y_{i} - \hat g_{p+1}^-(X_{i}) & \textif\ X_{i} < 0 \\
        Y_{i} - \hat g_{p+1}^+(X_{i}) & \otherwise
      \end{cases}
    \end{equation}
  \item Repeat the following steps $B_1$ times to produce a sequence of bootstrap
    estimates $\hat\tau_1^*,\dots,\hat\tau_{B_1}^*$. For the $k$th step:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M^-(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^-(b_n)\}$ and one of size $M^+(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^+(h_n)\}$. Let $\varepsilon_i^{*-}$ and
      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
      \begin{align}
        Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
        Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
      \end{align}
    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
      \begin{align}
        \hat\mu_-^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^-(h_n)} (Y_i^{*-} -
          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta_p (X_i^{*-})^p))^2 \\
        \hat\mu_+^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^+(h_n)} (Y_i^{*+} -
          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta_p (X_i^{*+})^p))^2
      \end{align}
    \item Save $\hat\mu_+^* - \hat\mu_-^*$ as $\hat\tau^*_k$.
    \end{enumerate}
  \item Estimate the bias as
    \begin{equation}
      \label{eq:2}
      \Delta^* = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k -
      \big[\hat g_{p+1}^+(0) - \hat g_{p+1}^-(0)\big]
    \end{equation}
  \end{enumerate}
\end{algorithm}
Obviously, the distribution of $\Delta^*$ depends on $B_1$ and we could
incorporate that dependency into our notation by wrting
$\Delta^*_{B_1}$. However, we will follow standard practice in the bootstrap
literature and assume that $B_1$ is large enough that it can be ignored and
define $\Delta^* = \plim_{B_1 \to \infty} \Delta^*_{B_1}$
